Response to reviewers

### 2024-11-28 Manuscript/ecography_reponse_letter.tex
Item 3

% \textbf{Item 3.}
%  In my opinion the primary issue in the manuscript lies in how the results are communicated
% As mentioned in the abstract and introduction, your objective is to evaluate the effectiveness of various functional diversity metrics in capturing patterns and signals associated with ten distinct processes linked to common community assembly mechanisms
% From what I understand, your aim is to offer a framework that assists ecologists in selecting the most appropriate diversity metric based on the relevant mechanism and observed patterns
% However, I believe this crucial message is not clearly conveyed
% Instead, the main takeaway from your results and their interpretation seems to be the high variability observed in the performance of the studied metrics.

% I recommend revising the results and discussion sections to address this issue more effectively
% Specifically, it would be helpful to provide a more detailed account of your main findings in the results section, particularly how different metrics performed in relation to the significance of your results, especially regarding the impact of data removal
% Additionally, a more thorough interpretation of these results is needed in the discussion (what really means that a specific metric deviate from the null model, and what the effect of data removal from 20\% to 80\% really implies)
% In the current manuscript, the discussion begins with an early focus on the limitations and caveats of your methods
% While acknowledging these aspects is important, it would be more effective to simplify this discussion and move it to a later section
% Instead, I would emphasize the interpretation of the performance of the various metrics to better communicate your main findings.

% We have now entirely reorganised the discussion section with clearer subsections:

% \begin{itemize} \tightlist \item   Results (including a subsection on empirical results) discussing in   more details the result
% Lines @@@
%  \item   Caveats: discussing clearly the caveats of our approach
% Lines @@@
%  \item   Box 2: ``so which metric do \textbackslash textit\{I\} choose?''   proposing a didactic approach and reflections to hopefully easily help   workers to choose their own metric
% Lines @@@ \end{itemize}

>>>>

\textcolor{blue}{\textbf{Item 3.}}
\textcolor{blue}{In my opinion the primary issue in the manuscript lies in how the results are communicated.
As mentioned in the abstract and introduction, your objective is to evaluate the effectiveness of various functional diversity metrics in capturing patterns and signals associated with ten distinct processes linked to common community assembly mechanisms.
From what I understand, your aim is to offer a framework that assists ecologists in selecting the most appropriate diversity metric based on the relevant mechanism and observed patterns.
However, I believe this crucial message is not clearly conveyed.
Instead, the main takeaway from your results and their interpretation seems to be the high variability observed in the performance of the studied metrics.}

\textcolor{blue}{I recommend revising the results and discussion sections to address this issue more effectively
Specifically, it would be helpful to provide a more detailed account of your main findings in the results section, particularly how different metrics performed in relation to the significance of your results, especially regarding the impact of data removal
Additionally, a more thorough interpretation of these results is needed in the discussion (what really means that a specific metric deviate from the null model, and what the effect of data removal from 20\% to 80\% really implies)
In the current manuscript, the discussion begins with an early focus on the limitations and caveats of your methods
While acknowledging these aspects is important, it would be more effective to simplify this discussion and move it to a later section
Instead, I would emphasize the interpretation of the performance of the various metrics to better communicate your main findings.}

We have now entirely reorganised the discussion section with clearer subsections:

\begin{itemize} 
  \item \textbf{Capturing approximated mechanisms with different metrics} discussing the simulated result in more details. Lines 369-405
  \item \textbf{Empirical results} focusing on the empirical results. Lines 407-448
  \item \textbf{Caveats} discussing clearly the caveats of our approach. Lines 450-505.
  \item  \textbf{Box 2: ``so which metric do \textit\{I\} choose?''} proposing a didactic approach and reflections to hopefully easily help workers to choose their own metric. Lines 506-553.
  \item \textbf{Conclusion} to briefly wrap up our findings. Lines 555-572.
\end{itemize}
